### 2020-12-05 paper/localpsf.tex
edited 3 slides. Edited paper intro more

The function $\varphi_x$ is the result of applying $\mathcal{A}$ to a point source, $\delta_x$, at some fixed point $x \in \Omega$, then translating the resulting impulse response function, $\mathcal{A}\delta_x$, to re-center it at zero instead of $x$. Locally translation invariant operators act like convolution operators locally, but the convolution kernel, $\varphi_x$, varies as $x$ changes. Locally translation invariant operators may therefore be approximated by spatially varying weighted sums of convolution operators of the form

@@

	\item The functions $w_i(x)$ are spatially varying weighting function that interpolate the convolution kernels $\varphi_i$.

@@

The core content of this paper is specifying (a) how we choose the points, $x_i$, (b) how we compute the convolution kernels, $\varphi_i$, and (c) what weighting functions $w_i$ that we use. Briefly, we compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a sum of point sources, $\delta_{x_i},$ at many points $x_i$ (a ``Dirac comb''). That is, we compute
\begin{equation*}
	\eta = \mathcal{A} \left(\sum_{i=1}^m \delta_{x_i}\right).
\end{equation*}
The batch of points $x_i$ are chosen so that the support of $\mathcal{A}\delta_{x_i}$ and the support of $\mathcal{A}\delta_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$. Since the impulse responses do not overlap, we may post-process $\eta$ to recover $\varphi_i$ for all of the points $x_i$ in the batch---by applying $\mathcal{A}$ to one vector, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until the approximation is sufficiently accurate or a maximum number of sample points is reached. The supports of the impulse responses $\mathcal{A}\delta_x$ are estimated a-priori, for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\mathcal{A}^T$ to a small number of constant, linear, and quadratic functions. This procedure for estimating the support of $\mathcal{A}\delta_x$ a-priori is the only part of the paper that requires non-negativity of the integral kernel. The functions $w_i$ are the defined as the smoothest functions, in a certain least-squares sense, that interpolate the points $x_i$.

@@

\subsection{Mean and covariance estimation}

>>>>

The function $\varphi_x$ is the result of applying $\mathcal{A}$ to a point source, $\delta_x$, at some fixed point $x \in \Omega$, then translating the resulting impulse response function, $\mathcal{A}\delta_x$, to re-center it at zero instead of $x$. Locally translation invariant operators act like convolution operators locally, but the convolution kernel, $\varphi_x$, varies as $x$ changes. We therefore approximate $\mathcal{A}$ by a spatially varying weighted sum of convolution operators of the form

@@

	\item The functions $w_i(x)$ are spatially varying weighting functions that interpolate the convolution kernels $\varphi_i$.

@@

Our approximation is defined by:
\begin{itemize}
	\item how we compute the convolution kernels, $\varphi_i$, (Section \ref{sec:get_impulse_response})
	\item how we choose the points, $x_i$, (Section \ref{sec:choosing_sample_points}) and 
	\item what weighting functions $w_i$ that we use (Section \ref{sec:weighting_functions}). 
\end{itemize}
To briefly summarize, we compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a sum of point sources, $\delta_{x_i},$ at many points $x_i$ (a ``Dirac comb''). That is, we compute
\begin{equation*}
	\eta = \mathcal{A} \left(\sum_{i=1}^m \delta_{x_i}\right).
\end{equation*}
The batch of points $x_i$ are chosen so that the support of $\mathcal{A}\delta_{x_i}$ and the support of $\mathcal{A}\delta_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$. Since the impulse responses do not overlap, we may post-process $\eta$ to recover $\varphi_i$ for all of the points $x_i$ in the batch---by applying $\mathcal{A}$ to one vector, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until the approximation is sufficiently accurate or a maximum number of sample points is reached. The supports of the impulse responses $\mathcal{A}\delta_x$ are estimated a-priori, for all $x \in \Omega$ simultaneously, via a procedure (described in Section \ref{eq:mean_and_covariance_estimation}) that involves applying $\mathcal{A}^T$ to a small number of constant, linear, and quadratic functions. This procedure is the only part of the paper that requires non-negativity of the integral kernel. The functions $w_i$ are the smoothest functions, in a least-squares sense, that interpolate the points $x_i$. Computing the functions $w_i$ require solving two Poisson PDEs per weighting function, and these PDE solves are done cheaply using multigrid.

@@

\subsection{Mean and covariance estimation}
\label{eq:mean_and_covariance_estimation}
